\documentclass[11pt,a4paper,sans]{moderncv} 
\moderncvstyle{classic}
\moderncvcolor{burgundy} 
\usepackage{lipsum} 
\usepackage{amsmath}
\usepackage[scale=0.88]{geometry}
\usepackage{array}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\setlength\extrarowheight{5pt}
\linespread{.7}

\firstname{Jaismin}
\familyname{Kaur}
\title{Sophomore, CSE  IIT Kanpur}
\email{jaismin@iitk.ac.in}
\mobile{+91 9453994598}

\begin{document}
\vspace*{-3.2\baselineskip}
\makecvtitle 
\vspace{-3.2\baselineskip}

\section{Education}

\begin{tabular}{|M{4cm}|M{5cm}|M{5.6cm}|M{4cm}|}
\hline
\begin{large}\textbf{Year}\end{large}&
\begin{large}\textbf{Degree/Certificate}\end{large} & 
\begin{large}\textbf{Institution}\end{large} &
\begin{large}\textbf{CPI/Marks(\%)}\end{large} \\
\hline
2015 - 2019 \small{(Expected)} & Bachelor of Technology,
Computer Science and Engineering & Indian Institute of Technology, Kanpur & 9.5/10 \\
\hline
2015 & CBSE (Class XII) & St. Theresa's Convent Sr. Sec. School, Karnal & 94\% \\ \hline
2013 & CBSE (Class X) & St. Theresa's Convent Sr. Sec. School, Karnal & 10/10 \\ \hline
\end{tabular}

\section{Achievements}

\cvitem{IIT JEE 2015}{\textbf{All India Rank 717} in JEE ADVANCED 2015 out of 150,000 students.}
\cvitem{KVPY 2014--15}{\textbf{Kishore Vaigyanik Protsahan Yojana}. Got selected for KVPY scholarship through an exam and interview.}
\cvitem{NTSE 2013--14}{\textbf{National Talent Search Examination}. Got selected for NTSE scholarship through a two level examination.}
\cvitem{NSEP 2014}{\textbf{National Standard Examination in Physics}. Got selected in top 1\%{} in National Standard Examination in Physics.}
\cvitem{Galaxy 2016}{\textbf{Best Artist Award} Recipient of Best Artist Award in Galaxy'16, cultural fest of IIT Kanpur.}

\section{Experience}

\renewcommand{\listitemsymbol}{-~}
\cventry{January'16--April'16}{Analysis and Experimenting Randomised Algorithms}{}{\newline $\cdot$ Analysed and experimented on randomised algorithms and their time complexities.\newline $\cdot$ Studied quick sort, skip list, ,random walk, binary search tree, Miller Rabin Test, and Polynomial Identity Testing.\newline $\cdot$ Coded and analysed the running time for a large number of inputs which varied in size}{}{}{}
\cventry{May'16--July'16}{Archetypal Analysis}{}{\newline $\cdot$ Scrutinised over data clustering and archetypal analysis on machine learning and data mining under \textbf{prof Piyush Rai}.\newline $\cdot$ Read papers on data clustering, neighborhood component analysis, archetypal analysis including weighted, robust analysis and probabilistic analysis}{}{}
\cventry{August'16--November'16}{Furnichair}{}{\newline $\cdot$ Designed and fabricated a prototype model of a multifunctional bench in TA201 course.\newline $\cdot$ The bench could serve the purpose of a table, arm chair, double seater, chair with side table and bed.\newline $\cdot$The final project included the technical drawings, the business plan, manufacturing using various manufacturing processes and the model}{}{}


\section{Technical skills}

\cvitem{Programming Languages}{GO, Python, Java, C, HTML/CSS, JavaScript}
\cvitem{Tools}{Git, Latex, Excel, Word}
\cvitem{Operating Systems}{Linux, Windows}
\cvitem{IDEs}{NetBeans, AndroidStudio}

\section{Relevant Courses}

\cvlistdoubleitem{Introduction to Programming}{Real Analysis}
\cvlistdoubleitem{Linear Algebra and ODE}{Discrete Mathematics}
\cvlistdoubleitem{Logic in Computer Science}{Abstract Algebra}
\cvlistdoubleitem{Introduction to Electronics}{Introduction to Electrical Engineering}
\cvlistdoubleitem{Computer Organisation\textsuperscript{*}}{Data Structures and Algorithms\textsuperscript{*}}
\cvitem{}{\small \textsuperscript{*}ongoing courses}
   
\section{Position of Responsibility}

\cvitem{2016--present}{\textbf{Student Guide}, Counseling Service, IIT Kanpur\newline $\cdot$ Mentoring a group of 4 new students into the institute by giving them academic, emotional as well as moral support.\newline $\cdot$ Ensured proper execution of the activities and sessions in the Orientation Program 2015 conducted for more than 800 freshmen.}
\cvitem{2016--present}{\textbf{Academic Mentor}, Counseling Service, IIT Kanpur\newline $\cdot$ Providing personal mentoring to the students weak in academics and guiding them through the course PHY102.}
\cvitem{2016--present}{\textbf{Secretary, Fine Arts Club}, Cultural Council, IIT Kanpur\newline $\cdot$ Organising various fine arts activities in the institute, including ArtFest, Antaragni, Exhibitions, Installations etc.}
\cvitem{January,2016--March,2016}{\textbf{Junior Executive, Public Relations, Techkriti'15},  IIT Kanpur\newline $\cdot$ Escorted keynote speakers through and to the events that took place in the  Technical and Entrepreneurship festival of IIT Kanpur.}

\section{Interests}

\renewcommand{\listitemsymbol}{-~}
\cvlistitem{Algorithms and Data Structures}
\cvlistitem{Artificial Intelligence}
\cvlistitem{Machine Learning}
\cvlistitem{Fine Arts and being creative!}

\end{document}\grid
\grid
\grid
